State of the Practice for Lattice Boltzmann Method Software

### 2022-10-02 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Revisions to sections 2.6 and 3.11 to explain AHP calculations in response to reviewer comments

\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{arydshln}
\usepackage{paralist}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{pbox}

@@

Once we measure each package, we still need to rank them to answer
\rqref{RQ_HighestQuality}. We do this via the Analytic Hierarchy Process (AHP),
a decision-making technique that compares multiple options by multiple criteria.
Our AHP algorithm uses the overall impression score, gathered via the
measurement template, to compare and rank the LBM software. AHP performs a
pairwise analysis using a matrix and generates an individual quality score for
each software package.  We have previously used this technique to rank software
in different domains, as in \citet{SmithEtAl2016}.

AHP focuses on relative comparisons, rather than requiring an unattainable
unified scale for measuring quality.  AHP starts with sets of $n$
\textit{options} and $m$ \textit{criteria}.  In our project there are 24
software products ($n=24$) and 9 criteria ($m = 9$).  To get a ranking for each
criterion, we perform a pairwise analysis between each of the options, in the
form of an $n \times n$ matrix $A$.  The value of $A_{jk}$ ranges from 1 to 9,
using the following definitions \citep{Saaty1980}:

@@

During our grading process we capture a subjective score, from one to ten, for
each package for each criterion.  To turn these into Saaty's pair-wise scores
for option $x$ versus option $y$, we use the following calculation for the
respective subjective scores $x_{\text{sub}}$ and $y_{\text{sub}}$:
\[
\begin{cases}
\min\{9, x_{\text{sub}} - y_{\text{sub}} + 1\} & x_{\text{sub}} \geq y_{\text{sub}} \\
1 / \min\{9, y_{\text{sub}} - x_{\text{sub}} + 1\} & x_{\text{sub}} < y_{\text{sub}}
\end{cases}
\]

For example, the installability for DL\_MESO and waLBerla is measured as $9$ and
$4$, respectively, so the score for DL\_MESO compared to waLBerla is 6 and
waLBerla compared to DL\_MESO is 1/6, as shown in Figure~\ref{}.

In our work, we make the common assumption of a reciprocal relationship between
options $k$ and $j$; that is, $A_{kj}=1/A_{jk}$.  A partial view of $A$ for the
quality of installability is found in Figure~\ref{}.  To obtain the overall
score for each option for a given criterion we use matrix $B$, where $B_{jk} =
A_{jk}/\sum_{i=1}^{i=n}(A_{i k})$.  That is, to get $B$ we normalize the columns
of $A$, as shown in Figure~\ref{}.  For a given quality, the score ($w_j$) for
software package $j$ is found by averaging the entries in row $j$ of $B$.  That
is, $w_j = \frac{1}{m} \sum_{i=1}^{i=m}(A_{j i})$. Besides providing a ranking,
the $w_j$ values can be combined for all qualities for an overall ranking, as
discussed in Section~\ref{Sec_OverallQuality}.

Figure

@@

Figure~\ref{Fig_OverallScore} shows the overall ranking. In the absence of other
information on priorities, we calculated the ranking by assuming an equal
weighting between all qualities. Software packages with an overall high score
ranked high in at least several of the individual qualities. ****TODO: Explain how
to combine rankings.****

>>>>

\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{arydshln}
\usepackage{paralist}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{pbox}
\usepackage{makecell}

@@

Once we measure each package, we still need to rank them to answer
\rqref{RQ_HighestQuality}. We do this via the Analytic Hierarchy Process (AHP),
a decision-making technique that compares multiple options by multiple criteria.
Our AHP algorithm uses the overall impression score, gathered via the
measurement template, along with pairwise comparisons between packages to rank
the LBM software. We have previously used this technique to rank scientific
software \citep{SmithEtAl2016}.

AHP focuses on relative comparisons, rather than requiring an unattainable
unified scale for measuring quality.  AHP starts with sets of $n$
\textit{options} and $m$ \textit{criteria}.  In our project there are 24
software products ($n=24$) and 9 qualities ($m = 9$).  To get a ranking for each
criterion, we perform a pairwise analysis between each of the options, in the
form of an $n \times n$ matrix $A$.  The value of $A_{jk}$ ranges from 1 to 9,
using the following definitions \citep{Saaty1980}:

@@

During our grading process we capture a subjective score, from one to ten, for
each package for each criterion.  To turn these into Saaty's pair-wise scores
for option $x$ versus option $y$, we use the following calculation from the
respective subjective scores $x_{\text{sub}}$ and $y_{\text{sub}}$:
\[
\begin{cases}
\min\{9, x_{\text{sub}} - y_{\text{sub}} + 1\} & x_{\text{sub}} \geq y_{\text{sub}} \\
1 / \min\{9, y_{\text{sub}} - x_{\text{sub}} + 1\} & x_{\text{sub}} < y_{\text{sub}}
\end{cases}
\]

\noindent For example, we measured the installability for DL\_MESO and waLBerla 
as $9$ and $4$, respectively; therefore, on the 9-point scale, DL\_MESO compared to
waLBerla is 6 and waLBerla compared to DL\_MESO is 1/6, as shown in the sample
AHP calculations (Table~\ref{Tbl_SampleAHP}).

In our work, we make the common assumption of a reciprocal relationship between
options $k$ and $j$; that is, $A_{kj}=1/A_{jk}$.  A partial view of $A$ for the
quality of installability is found in Table~\ref{Tbl_SampleAHP}.  To obtain the
overall score for each option for a given criterion we use matrix $B$, where
$B_{jk} = A_{jk}/\sum_{i=1}^{i=n}(A_{i k})$.  That is, to get $B$ we normalize
the columns of $A$ by dividing by the sum of the entries in the column, as shown
in Table~\ref{Tbl_SampleAHP}.  For a given quality, the score ($s_j$) for
software package $j$ is found by averaging the entries in row $j$ of $B$.  That
is, $s_j = \frac{1}{n} \sum_{i=1}^{i=n}(B_{j i})$, as shown in the final column
of Table~\ref{Tbl_SampleAHP}. Sorting the $s_j$ values provides a ranking for
the software packages for the quality under investigation.  The $s_j$ values can
be combined for all qualities for an overall ranking, as discussed in
Section~\ref{Sec_OverallQuality}.

\begin{table}[h!]
\begin{center}
\begin{tabular}{ l c c c c c | c c c c c | c }
 %\toprule
 ~ & \multicolumn{5}{l}{A Matrix} & \multicolumn{5}{l}{BMatrix} & ~\\
 \midrule
 ~ & \rotatebox{90}{DL\_MESO} & \rotatebox{90}{waLBerla} & \rotatebox{90}{SunlightLB} & $\cdots$ & \rotatebox{90}{Musubi} & \rotatebox{90}{DL\_MESO} & \rotatebox{90}{waLBerla} & \rotatebox{90}{SunlightLB} & $\cdots$ & \rotatebox{90}{Musubi} & AVG \\
 \midrule
 DL\_MESO (LBE) & 1 & 6 & 3 & $\cdots$ & 2 & 0.0691 & 0.0622 & 0.0808 & $\cdots$ & 0.0808 & 0.072\\
 waLBerla & 1/6 & 1 & 1/4 & $\cdots$ & 1/5 & 0.0115 & 0.0104 & 0.0067 & $\cdots$ & 0.0067 & 0.009\\
 SunlightLB & 1/3 & 4 & 1 & $\cdots$ & 1/2 & 0.0230 & 0.0415 & 0.0269 & $\cdots$ & 0.0269 & 0.031\\
 $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\ddots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\ddots$ & $\vdots$ & $\vdots$\\
 Musubi & 1/2 & 5 & 2 & $\cdots$ & 1 & 0.0345 & 0.0518 & 0.0539 & $\cdots$ & 0.0539 & 0.048\\  
 \midrule
 SUM = & 14.48 & 96.50 & 37.12 & $\cdots$ & 23.78 & 1.000 & 1.000 & 1.000 & $\cdots$ & 1.000 & 1.000\\
 \bottomrule
\end{tabular}
\end{center}
\caption{Sample AHP Calculations for the Quality of Installability} \label{Tbl_SampleAHP}
\end{table}

@@

Figure~\ref{Fig_OverallScore} shows the overall ranking. The AHP method finds
the weighting of quality $i$ ($w_i$) in the same way that the score ($s_j$) was
found for software package $j$ evaluated for a given quality
(Section~\ref{AHP}).  That is, we conduct a pairwise comparison between the
priority of different qualities to construct the $m \times m$ matrices $A$ and
$B$ and then we average row $i$ of matrix $B$ to find the priority value $w_i$
for quality $i$.  If we introduce the notation that $s^i_j$ is the score for
quality $i$ for package $j$, then the overall score $S_j$ for package $j$ is
found via:

$$S_j = \sum_{i=1}^m s^i_j w_i$$

In the absence of other information on priorities, we calculated the ranking by
assuming an equal weighting between all qualities. Software packages with an
overall high score ranked high in at least several of the individual qualities.
